---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# colordew

<!-- badges: start -->
`r lifecycle::badge('experimental')`
<!-- badges: end -->

The goal of colordew is to provide a color palette for plotting in R, based on the colors of the game Stardew Valley. We aim to have color palettes for a variety of seasons, characters, holidays, and locations.

## Installation

You can install the development version of colordew from [GitHub](https://CRAN.R-project.org) with:

``` r
remotes::install_github("aftonsteps/colordew")
```

## Example

TODO!

```{r example}
## library(colordew)
## basic example code
```

## Contributing
Please see the `CONTRIBUTING` guide for how to add to this package.

## Code of Conduct

Please note that the colordew project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
